### 2012-03-19 GUIErrorDetector/paper/review/response.txt

Thanks for your helpful comments.

We agree with reviewer #1 and #2 that this paper addresses one kind of
error (i.e., the invalid thread access error) in GUI application.
However, as shown in Sec 1.2, this error is important, pervasive, and
severe in developing multithreaded GUI applications, and there are no
effective solutions yet. As part of this paper’s contribution is
identifying the invalid thread access problem. We keep our solution
simple to make it generally applicable and sufficient to detect many
real errors [*is such argument useful?*], instead of focusing on finding
certain sophisticated errors. On the other hand, the core idea of
formulating invalid thread access error detection as source-sink
reachability analysis can be extended to other domains, such as finding
Null pointer errors (does a null pointer reach a dereference?), security
vulnerability (does a tainted input reach a security-critical operation?),
or IO-related errors (e.g., does a closed file reach a read operation?).

Reviewer #1 requests additional clarification for Sec. 4.3.4. Here,
by “sound” graph visit algorithm, we mean one that will not miss any true
error path. Given a conservative call graph, BFS and DFS are not sound,
because BFS returns the shortest path and DFS returns the first path it
sees when searching in deep of the graph.  Both of them may return the
false positive paths or miss the true error paths.  We agree that exhaustive
search may not report the exact error path as it appears at runtime, since
static graph traversal cannot precisely reason about the number of loops a
real program execution may take. However, exhaustive path enumeration is
still sound in that it will not miss error paths, since it lists all
non-cyclic paths from a starting node to UI-accessing nodes via thread
spawning node (i.e., Thread.start()), even if a UI-accessing or thread
spawning node is in a cycle. [*I am not quite satisfied with this argument,
but not sure how to make it better*]

### 2012-03-19 trunk/GUIErrorDetector/paper/review/response.txt

Thanks for your helpful comments.

We agree with reviewer #1 and #2 that this paper addresses one kind of
error (i.e., the invalid thread access error) in GUI application.
However, as shown in Sec 1.2, this error is important, pervasive, and
severe in developing multithreaded GUI applications, and there are no
effective solutions yet. As part of this paper's contribution is
identifying the invalid thread access problem. We keep our solution
simple to make it generally applicable and sufficient to detect many
real errors [*is such argument useful?*], instead of focusing on finding
certain sophisticated errors. On the other hand, the core idea of
formulating invalid thread access error detection as source-sink
reachability analysis can be extended to other domains, such as finding
Null pointer errors (does a null pointer reach a dereference?), security
vulnerability (does a tainted input reach a security-critical operation?),
or IO-related errors (e.g., does a closed file reach a read operation?).

Reviewer #1 requests additional clarification for Sec. 4.3.4. Here,
by "sound" graph visit algorithm, we mean one that will not miss any true
error path. Given a conservative call graph, BFS and DFS are not sound,
because BFS returns the shortest path and DFS returns the first path it
sees when searching in deep of the graph.  Both of them may return the
false positive paths or miss the true error paths.  We agree that exhaustive
search may not report the exact error path as it appears at runtime, since
static graph traversal cannot precisely reason about the number of loops a
real program execution may take. However, exhaustive path enumeration is
still sound in that it will not miss error paths, since it lists all
non-cyclic paths from a starting node to UI-accessing nodes via thread
spawning node (i.e., Thread.start()), even if a UI-accessing or thread
spawning node is in a cycle. [*I am not quite satisfied with this argument,
but not sure how to make it better*]

### 2012-03-20 GUIErrorDetector/paper/review/response.txt

We thank the reviewers for their comments.

We agree that our technique is simple -- but we view elegance as a positive
rather than a negative!  Part of our contribution is the observation that
an approach, which is easy to understand and to verify, is also effective
in solving an important problem that plagues real developers.

A reviewer asked why breadth/depth first search is not sound.  The reason
is that breadth/depth first search visits every node, but does not traverse
every path to visit that node.  For example, suppose that there exists some
fault-revealing path between entry node E and UI-access node U.  A sound
algorithm is one that reports a fault-revealing path between entry node E
and UI-access node U.  An unsound algorithm might report an infeasible (and
therefore non-fault-revealing) path between the nodes.  Figure 8 gives a
concrete example:  for the graph of Figure 8(b), a shortest-path
(depth-first) algorithm does report a path between entry() and uiAcc(), but
not one that reveals the problem.  We can clarify this issue in the paper.

With regard to applicability and generalization, we agree that we have
applied our technique to one specific (but important) problem.  There is a
rich history of testing and analysis problems being cast as reachability
(the work of Tom Reps is one example).  We believe that other problems,
such as detecting security vulnerabilities, can also be formulated as path
reachability.

### 2012-03-21 trunk/GUIErrorDetector/paper/review/response.txt

We thank the reviewers for their comments.

We agree that our technique is simple -- but we view elegance as a positive
rather than a negative!  Part of our contribution is the observation that
an approach, that is easy to understand and to verify, is also effective
in solving an important problem that plagues real developers.

A reviewer asked why breadth/depth first search is not sound.  The reason
is that breadth/depth first search visits every node, but does not traverse
every path to visit that node.  For example, suppose that there exists some
fault-revealing path between entry node E and UI-access node U.  A sound
algorithm is one that reports some fault-revealing path between entry node
E and UI-access node U.  An unsound algorithm might report an infeasible
(and therefore non-fault-revealing) path between the nodes.  Figure 8 gives
a concrete example:  for the graph of Figure 8(b), a shortest-path
(depth-first) algorithm does report a path between entry() and uiAcc(), but
not one that reveals the problem.  We can clarify this issue in the paper.

With regard to applicability and generalization, we agree that we have
applied our technique to one specific (but important) problem.  There is a
rich history of testing and analysis problems being cast as reachability
(the work of Tom Reps is one example).  We believe that other problems,
such as detecting security vulnerabilities, can also be formulated as path
reachability.  We have not done so in the current paper.

### 2012-04-23 GUIErrorDetector/paper/evaluation.tex
Improve formatting

\begin{figure}[t]
  \centering
  \includegraphics[scale=0.45]{cgexample}
  \vspace*{-5.0ex}\caption {{\label{fig:ex} (a) shows example code, in which
\CodeIn{safe()} is a Safe UI method, and \CodeIn{uiAcc()} is a UI-accessing method.
(b) shows a less precise call graph built by RTA or 0-CFA, and (c) shows a more
precise call graph built by 1-CFA. Nodes for constructors are omitted for brevity.
Using the less precise call graph, our error
detection algorithm (Figure~\ref{fig:detectalgorithm}) reports an invalid method
call chain: \CodeIn{entry()}
$\rightarrow$ \CodeIn{f()} $\rightarrow$ \CodeIn{start()} $\rightarrow$ \CodeIn{run()}
$\rightarrow$ \CodeIn{uiAcc()}. It does not report
the actual error path because it is longer: \CodeIn{entry()} $\rightarrow$ \CodeIn{g1()} $\rightarrow$
\CodeIn{g2()} $\rightarrow$ \CodeIn{start()} $\rightarrow$ \CodeIn{run()} $\rightarrow$ \CodeIn{uiAcc()}.
The algorithm outputs the actual error path when using the more precise call graph.
}}
\end{figure}

>>>>

\begin{figure}[t]
  \centering
  \includegraphics[scale=0.45]{cgexample}
  \vspace*{-5.0ex}\caption {{\label{fig:ex} (a) shows example code, in which
\CodeIn{safe()} is a Safe UI method, and \CodeIn{uiAcc()} is a UI-accessing method.
(b) shows a less precise call graph built by RTA or 0-CFA, and (c) shows a more
precise call graph built by 1-CFA. Nodes for constructors are omitted for brevity.
\newline
Using the less precise call graph, our error
detection algorithm (Figure~\ref{fig:detectalgorithm}) reports an invalid method
call chain: \CodeIn{entry()}
$\rightarrow$ \CodeIn{f()} $\rightarrow$ \CodeIn{start()} $\rightarrow$ \CodeIn{run()}
$\rightarrow$ \CodeIn{uiAcc()}. It does not report
the actual error path because it is longer: \CodeIn{entry()} $\rightarrow$ \CodeIn{g1()} $\rightarrow$
\CodeIn{g2()} $\rightarrow$ \CodeIn{start()} $\rightarrow$ \CodeIn{run()} $\rightarrow$ \CodeIn{uiAcc()}.
The algorithm outputs the actual error path when using the more precise call graph.
}}
\end{figure}
